SDR enhancement by clouds \\\large{An analysis}

### 2023-11-28 article/article.tex
Commit 2023-11-28 19:13

\begin{frontmatter}
\title{SDR enhancement by clouds \\\large{A Short Subtitle} }
\author[1]{Athanasios Natsis%
\corref{cor1}%
\fnref{fn1}}
 \ead{natsisphysicist@gmail.com} 
\author[2]{Alkiviadis Bais%
%
\fnref{fn2}}
 \ead{abais@auth.gr} 
\author[1]{Charikleia Meleti%
%
\fnref{fn3}}
 \ead{meleti@auth.gr}

@@

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, breakable, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced]}{\end{tcolorbox}}\fi

@@

Clear sky identification

\begin{itemize}
\tightlist
\item
  helps on determining thresholds
\end{itemize}

Criteria for enhancement based on TSI

\begin{itemize}
\tightlist
\item
  some other were tested
\end{itemize}

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, left=2mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, leftrule=.75mm, toprule=.15mm, coltitle=black, titlerule=0mm, arc=.35mm, opacitybacktitle=0.6, bottomtitle=1mm, breakable, colframe=quarto-callout-important-color-frame, opacityback=0, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colback=white, toptitle=1mm]

@@

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

Equation~\ref{eq-lowbap}

\citep{Bais1997}

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \begin{equation}\protect\hypertarget{eq-lowbap}{}{ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
}\label{eq-lowbap}\end{equation}

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

>>>>

\begin{frontmatter}
\title{SDR enhancement by clouds \\\large{An analysis} }
\author[1]{Athanasios Natsis%
\corref{cor1}%
\fnref{fn1}}
 \ead{natsisphysicist@gmail.com} 
\author[2]{Alkiviadis Bais%
%
\fnref{fn2}}
 \ead{abais@auth.gr} 
\author[1]{Charikleia Meleti%
%
\fnref{fn3}}
 \ead{meleti@auth.gr}

@@

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{clear-sky-identification}{%
\subsection{Clear sky identification}\label{clear-sky-identification}}

Use it to find some interesting days to manual check the CE thresholds.
No other usage of clear/cloud characterization in CE.

\hypertarget{criteria-for-enhancement-based-on-tsi}{%
\subsection{Criteria for enhancement based on
TSI}\label{criteria-for-enhancement-based-on-tsi}}

Many have used models or some statistical method to determine then CE
thresholds.

\ldots\ldots. cite \ldots\ldots{} Descriptions

We used as reference the \ldots. extraterrestrial horizontal irradiance
\ldots..

\[
\text{ETH} = \cos(\theta) \times \text{TSI}_\text{TOA}
\]

\begin{equation}\protect\hypertarget{eq-CEcrit1}{}{
\text{GHI} > 0.8 \times \text{ETH} + 20\,Wm^{-2}
}\label{eq-CEcrit1}\end{equation}

Where GHI sddsfa

\begin{itemize}
\tightlist
\item
  some other were tested Equation~\ref{eq-CEcrit1}
\end{itemize}

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, leftrule=.75mm, colframe=quarto-callout-important-color-frame, breakable, coltitle=black, rightrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, colbacktitle=quarto-callout-important-color!10!white, arc=.35mm, toptitle=1mm, left=2mm, bottomtitle=1mm, bottomrule=.15mm, titlerule=0mm, opacitybacktitle=0.6, opacityback=0, colback=white]

@@
